### 2016-07-18 paper/paper.tex
Initialize paper

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\begin{document}

\title{Network Cascades}
\author{Marco Brack \and Carsten Hartenfels}
\maketitle

\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. \cite{simplemodel}
\end{abstract}

\section{Motivation}

\section{Modeling Network Cascades}

\section{Ongoing Research}

\bibliography{paper}
\bibliographystyle{plain}

\end{document}

### 2016-07-22 bibliography/draw-citations.sh
Systematize the bibliography

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+dot -Tpng bibliography.dot > bibliography.png

### 2016-07-22 bibliography/grab-papers.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+wget -O papers/watts2002simple.pdf http://www.stat.berkeley.edu/~aldous/260-FMIE/Papers/watts.pdf
+wget -O papers/newman2003structure.pdf http://epubs.siam.org/doi/pdf/10.1137/S003614450342480

### 2016-07-22 bibliography/grab-papers.sh
Fix paper grabbery and add Milgramery

@@ -1,4 +1,12 @@
-#!/bin/bash
-
-wget -O papers/watts2002simple.pdf http://www.stat.berkeley.edu/~aldous/260-FMIE/Papers/watts.pdf
-wget -O papers/newman2003structure.pdf http://epubs.siam.org/doi/pdf/10.1137/S003614450342480
+#!/usr/bin/perl
+use List::Util qw(pairs);
+@PAPERS = qw(
+    watts2002simple         http://www.stat.berkeley.edu/~aldous/260-FMIE/Papers/watts.pdf
+    newman2003structure     http://epubs.siam.org/doi/pdf/10.1137/S003614450342480
+    milgram1969note         https://www.dropbox.com/s/ij30vedzdinljpo/milgram1969note.pdf?raw=1
+);
+for (pairs @PAPERS) {
+    ($name, $url) = @$_;
+    $file = "papers/$name.pdf";
+    system 'wget', '-O', $file, $url unless -e $file;
+}

### 2016-07-22 bibliography/grab-papers.sh
Add karimi2013temporal

@@ -2,3 +2,6 @@
 
 wget -O papers/watts2002simple.pdf http://www.stat.berkeley.edu/~aldous/260-FMIE/Papers/watts.pdf
 wget -O papers/newman2003structure.pdf http://epubs.siam.org/doi/pdf/10.1137/S003614450342480
+
+echo "Download manually:"
+echo "karimi2013temporal: https://link.springer.com/chapter/10.1007/978-3-642-36461-7_16"

### 2016-07-22 bibliography/grab-papers.sh
Add watts1999small

@@ -4,6 +4,7 @@ use List::Util qw(pairs);
     watts2002simple         http://www.stat.berkeley.edu/~aldous/260-FMIE/Papers/watts.pdf
     newman2003structure     http://epubs.siam.org/doi/pdf/10.1137/S003614450342480
     milgram1969note         https://www.dropbox.com/s/ij30vedzdinljpo/milgram1969note.pdf?raw=1
+    watts1999small          http://blacky.terra32.net/trusso/CorsoTeoriaAvanzataReti/info4/altrecose/DuncanJWattsSigma.pdf
 );
 for (pairs @PAPERS) {
     ($name, $url) = @$_;

### 2016-07-22 bibliography/grab-papers.sh
Add kempe2003maximizing

@@ -5,6 +5,7 @@ use List::Util qw(pairs);
     newman2003structure     http://epubs.siam.org/doi/pdf/10.1137/S003614450342480
     milgram1969note         https://www.dropbox.com/s/ij30vedzdinljpo/milgram1969note.pdf?raw=1
     watts1999small          http://blacky.terra32.net/trusso/CorsoTeoriaAvanzataReti/info4/altrecose/DuncanJWattsSigma.pdf
+    kempe2003maximizing     http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.407.4750&rep=rep1&type=pdf
 );
 for (pairs @PAPERS) {
     ($name, $url) = @$_;

### 2016-08-22 paper/paper.tex
Use proper template for paper
Add some sections
Adopt structure from presentation for paper

@@
-\documentclass{article}
-
+\documentclass{sig-alternate-05-2015}
 \usepackage[utf8]{inputenc}
 \usepackage{graphicx}
+
+\acmPrice{how did this get here i am not good with computer}
 
@@
 \title{Network Cascades}
+\subtitle{WattsApp With Those}
 \author{Marco Brack \and Carsten Hartenfels}
@@
 \begin{abstract}
-  Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-\cite{simplemodel}
+Concrete.
 \end{abstract}
 
-\section{Motivation}
+\section{Motivation}\label{sec:motivation}
 
-\section{Modeling Network Cascades}
+Since caveman times people have been wondering how the ball gets rolling.
 
-\section{Ongoing Research}
+Communication technologies, such as Skype or WhatsApp, need users to actually be useful for communication between them.
+But how do these applications gain users in the first place then?
+They are mutually incompatible with each other, so surely if no one is using them, there is no reason for other people to start using them either.
 
+One way to explain these phenomena is \emph{network cascades}.
+To stick with the high-level example above, assume that one person starts to use some communication technology.
+Then they tell their friends about it, convincing some of them to also begin using the application to communicate.
+Those friends to the same with their own friends, and so on and so forth.
+Given a suitably connected social network and a high enough ``convincability'' of its members, the usage will cascade through the entire network and eventually spread to all, or at least most, of its members.
+On the other hand, if the network does not have the required connectivity or if important bridge members cannot be convinced of the switch, the cascade may be halted and will not cause a global change in adoption.
+
+How to model these network cascades and what properties enable global cascades is the topic of the paper ``A simple model of global cascades on random networks'' by Duncan J.
+Watts\cite{simplemodel}.
+In this seminar paper, we will attempt to explain the contents of that paper in an effort to make the topic understandable to our fellow students.
+
+\par\bigskip
+
+Section \ref{sec:model} presents a simple network cascade model as laid out by Watts\cite{simplemodel}.
+
+\section{Model}\label{sec:model}
+
+The following section details Watts' simple model of network cascades\cite{simplemodel}.
+It explains the theoretical foundation and links it to the high-level example given in section \ref{sec:motivation}.
+
+The model deals with a network of $n \in \mathbb{N}$ \emph{agents}.
+These agents are represented as nodes in a random graph.
+In regards to the example from section \ref{sec:motivation}, these agents represent people.
+
+Each of these agents is connected to $k \in \mathbb{N}$ other nodes with a probability of $p_k \in [0,1]$.
+These edges represent the neighbors that each node observes, or in the example's terms, the person's friends.
+
+Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution TODO with some weird integral property.
+Relating to the example, this represents the ``convincability'' of a person.
+
+Finally, all agents are given a state $\in \left\lbrace 0, 1 \right\rbrace$, which is initially set to $0$ for all notes.
+In the example's case, a state of $1$ represents a user of the communication application and a value of $0$ represents someone not using it.
+
+Now the model is simulated over a time $t$, starting with $0$.
+At a random point in time, the state of a single node is changed to $1$.
+This is analogous to the first person starting to use the application.
+
+In independent random intervals, each node with state $0$ checks the state of all its neighbors.
+If the ratio of neighbors with states $1$ is greater than or equal to the node's threshold $\phi$, it will also change its state to $1$.
+This is the act of a person being ``convinced'' to begin using the application because enough of their friends are using it as well.
+
+However, an agent with state $1$ will never switch back to state $0$.
+This does not directly map to a concept in a real-world example, as people may stop using an application at a later time.
+See also section \ref{sec:threats}.
+
+\section{Example}\label{sec:example}
+
+\section{Threats to Validity}\label{sec:threats}
+
+This section points out the possibly invalid points in Watts' paper\cite{simplemodel}, as well as the limitations with the model presented therein.
+
+One limitation already mentioned in section \ref{sec:model} is that the model only allows any agent to switch its state a single time.
+It also lacks states beyond the binary $0$ and $1$.
+These make it difficult or impossible to model cascades that involve more than a single option, such as multiple competing products.
+
+It also does not take into account relationship strength or authority.
+Every neighbor of a node always has the same weight and only the amount of neighbors with a certain state matters.
+However, this is far removed from a social network, where the persuasive power varies greatly depending on the kind of relationship between two people.
+
+Any kind of personal knowledge or observation of a global adoption rate is not taken into account either.
+A cascade is always started by a single node switching its state, while in reality, several people might decide to switch without their friends directly prompting them to do so.
+
+TODO: bimodality with one sample
+
+Finally, the paper itself does not have a section on threats to validity. TODO: yo dawg I heard you like to write papers so I'll cite a paper about writing papers so you can read while you write
+
+\bibliographystyle{abbrv}
 \bibliography{paper}
-\bibliographystyle{plain}
 

### 2016-08-22 paper/paper.tex
Explain the weird integral property

@@
 
-Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution TODO with some weird integral property.
+Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution $f(\phi): [0,1] \rightarrow [0,1]$ which must be normalized such that $\int_0^1 f(\phi) d\phi = 1$, i.e.
+the area beneath the propability function is 1, which means that all distributions must allocate the same total of propabilities, which makes them comparable among each other.
 Relating to the example, this represents the ``convincability'' of a person.

### 2016-08-22 paper/paper.tex
Add some TODOs
Nevermind
Explain the network model

@@
 
+% TODO: At least one more example
+
 How to model these network cascades and what properties enable global cascades is the topic of the paper ``A simple model of global cascades on random networks'' by Duncan J.
@@
 These edges represent the neighbors that each node observes, or in the example's terms, the person's friends.
+$p_k$ is poisson-distributed: $p_k = \frac{e^{-z}z^k}{k!}$, with $z = \left<k\right>$ being the expectation-value of $p_k$ (the average degree).
+
+This random network model is equivalent to an Erdős–Rényi-Model with $p = \frac{z}{n}$.
+Networks following the Erdős–Rényi-Model are build by creating $n$ nodes and creating each possible edge with a propability $p$.
+This method generates networks which have a small average distances between nodes and a low amount of clustering.
 
@@
 \section{Example}\label{sec:example}
+
+\section{Findings}\label{sec:findings}
 

### 2016-08-22 paper/paper.tex
Examplarize the shit out of the model (part 1)

@@
 
+Relating this to the example, this might mean that Alice, Bob, Charly and Dave are ``agents'' who are faced with the decision if they should jump on the WhatsApp bandwagon and are thus each represented as a node in the network.
+
 Each of these agents is connected to $k \in \mathbb{N}$ other nodes with a probability of $p_k \in [0,1]$.
@@
 
+In our example, we choose $z$ to be 2.
+This means that the graph of the degree distribution for $p_k$ has its peak at 2 and that we would expect that most nodes have 2 neighbors.
+Plugging that into the distribution function tells us that the propability for this case (2 neighbors) is about $27\%$, and the propability for 1 neighbor is $27\%$, $18\%$ for 3 neighbors, $9\%$ for 4 and $3\%$ for 5, and so on.
+According to this, a ``realistic'' network for our potential WhatsApp users might have an connection between Alice and Bob, between Bob and Charly, and Charly and Dave, leaving Alice and Dave with each one neighbour, and Bob and Charly with each two neighbors.
+
 This random network model is equivalent to an Erdős–Rényi-Model with $p = \frac{z}{n}$.
@@
 This method generates networks which have a small average distances between nodes and a low amount of clustering.
+
+In the example, there are $n = 4$ nodes.
+With $z = 2$ $p$ is $\frac{2}{4} = 0.5$, so we would expect half of all possible edges to exist.
+There are 6 possible edges in the network (this is excluding edges from a node to itself), and we chose to create 3, so our example indeed conforms perfectly to the Erdős–Rényi-Model.
 

### 2016-08-22 paper/paper.tex
Examplarize the integral restriction

@@
 Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution $f(\phi): [0,1] \rightarrow [0,1]$ which must be normalized such that $\int_0^1 f(\phi) d\phi = 1$, i.e.
-the area beneath the propability function is 1, which means that all distributions must allocate the same total of propabilities, which makes them comparable among each other.
+the area beneath the propability function is 1, which means that all distributions must allocate the same total of propabilities.
+This restriction is necessary because we are assigning a propability to mutually exclusive ``events''.
 Relating to the example, this represents the ``convincability'' of a person.
+
+The integral restriction is more easily understandable in a discrete case. For our WhatsApp example, we define the following discrete propability distribution:
+
+$
+f(\phi) =
+  \begin{cases}
+    0 & \phi \in {0, 1} \\
+    0.1 & \phi \in {0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9} \\
+    0.2 & \phi in {0.5}
+  \end{cases}
+$
+
+This means that the thresholds $0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9$ all have a propability of $10\%$ to be chosen, the threshold $0.5$ has a chance of $20\%$, and 0 and 1 will not be chosen at all.
+In contrast, we could assign a propability of $100\%$ to the threshold 0 and $0\%$ to all other thresholds and would still conform to the integral restriction.
 

### 2016-08-22 paper/paper.tex
Finish the example in the model section

@@
 
+%TODO: Image
+
 This random network model is equivalent to an Erdős–Rényi-Model with $p = \frac{z}{n}$.
@@
   \begin{cases}
-    0 & \phi \in {0, 1} \\
-    0.1 & \phi \in {0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9} \\
-    0.2 & \phi in {0.5}
+    0 & \phi \in \{0, 1\} \\
+    0.1 & \phi \in \{0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9\} \\
+    0.2 & \phi \in \{0.5\}
   \end{cases}
@@
 See also section \ref{sec:threats}.
+
+In the example with Alice and the others, we apply the first propability distribution from above.
+Let's say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the propability is $20\%$), Charly is assigned $\phi_{Charly} = 0.3$ and Dave $\phi_{Dave} = 0.9$.
+This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it (switch his state to $1$), whereas Charly already switches if only $30\%$ of his neighbors adopt the technology.
+Since Dave has only 1 neighbor, Charly, he switches as soon as Charly switches (in this case, $100\%$ of his neighbors would have switched).
+Dave has two neighbors, Bob and Dave, but only needs $30\%$ to switch, so it suffices if either Bob or Dave switch (that would be $50\%$ of his neighbors).
 

### 2016-08-23 paper/paper.tex
Start describing cascade condition stuff

@@
 \usepackage{graphicx}
+\usepackage{csquotes}
 
@@
 Now the model is simulated over a time $t$, starting with $0$.
-At a random point in time, the state of a single node is changed to $1$.
+At a random point in time, the state of a single node (the seed) is changed to $1$.
 This is analogous to the first person starting to use the application.
@@
 \section{Example}\label{sec:example}
+
+\section{Cascade Condition}\label{sec:section}
+
+Watts claims that global cascades are only possible if \textquote{the largest vulnerable cluster percolates}. This is called the \emph{cascade condition}.
+
+A node is vulnerable if its threshold is low enough so that only one of it's neighbors needs to switch state for it to switch state itslef.
+Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''.
+A vulerable cluster is a connected set of nodes that all switch state if a contained ``early adopter'' adjacent to an ``innovator'' switches its state.
+This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.
 

### 2016-08-24 paper/cascade-condition.rb
Add script for calculating cascade windows

@@ -1,0 +1,61 @@
+ITERATIONS = 69
+
+def factorial(n)
+  n == 0 ? 1 : n*factorial(n-1)
+end
+
+# Returns the propability that a node with degree k is vulerable for a homogenous threshold phi
+def rho_homo(phi, k)
+  return k == 0 || phi <= 1.to_f/k ? 1 : 0
+end
+
+# Returns the propability that a node has degree k for a poisson-distibiution of degrees with mean z
+def p_poisson(z, k)
+  (Math::E ** -z * z ** k) / factorial(k)
+end
+
+# That cryptic G_0''(1) function
+def cascade(phi, z)
+  (0..ITERATIONS).inject(0){ |sum, k| sum + k * (k - 1) * rho_homo(phi, k) * p_poisson(z, k) }
+end
+
+def cascade_condition(phi, z)
+  cascade(phi, z) > z
+end
+
+
+puts "Cascade condition for z from 20 to 0 and phi from 0.1 to 0.3"
+puts "██: Cascades possible. ░░: Cascades not possible"
+puts
+
+z = 20
+while (z >= 0) do
+  print sprintf('%02d', z)
+  phi = 0.1
+  while (phi <= 0.3) do
+    print cascade_condition(phi, z) ? "██" : "░░"
+    phi += 0.01
+  end
+  puts
+  z -= 1
+end
+puts "  0.1                ...                0.3"
+
+
+puts ""
+puts "First iterations for z = 2 and phi=0.2"
+
+7.times do |k|
+  puts "#{k} * #{k-1} * #{rho_homo(0.2, k)} * #{p_poisson(2, k).round(3)} = #{(k * (k - 1) * rho_homo(0.2, k) * p_poisson(2, k)).round(3)}"
+end
+
+puts "Sum: #{cascade(0.2, 2).round(3)}"
+
+puts ""
+puts "First iterations for z = 8 and phi=0.2"
+
+7.times do |k|
+  puts "#{k} * #{k-1} * #{rho_homo(0.2, k)} * #{p_poisson(8, k).round(3)} = #{(k * (k - 1) * rho_homo(0.2, k) * p_poisson(8, k)).round(3)}"
+end
+
+puts "Sum: #{cascade(0.2, 8).round(3)}"

### 2016-08-24 paper/generating-functions.tex
Add some informal notes

Example for an Propability Generating Function: The PGF for a dice throw:

\begin{equation*}
\begin{split}
P(x)\\
&= 0x^0 + \frac{1}{6}x^1 + \frac{1}{6}x^2 + \frac{1}{6}x^3 + \frac{1}{6}x^4 + \frac{1}{6}x^5 + \frac{1}{6}x^6\\
&= \sum_{eyes=1}^{6}\frac{1}{6}x^{eyes}
\end{split}
\end{equation*}

The coefficients of $x^eyes$ are the propability for $eyes$ as the result of the dice-throw. For a PGF, if $x=1$, the PGF must equal to $0$:

\begin{equation*}
\begin{split}
P(X)\\
&= \frac{1}{6} + \frac{1}{6} + \frac{1}{6} + \frac{1}{6} + \frac{1}{6} + \frac{1}{6}\\
&= 1
\end{split}
\end{equation*}

For another example let's express the degree-distibution of a network with a poisson-distribution with the peak at $z = 5$ neighbors.

\begin{multline*}
\begin{split}
P(x)\\
= \sum_{k=0}^{\infty}\frac{e^{-5}5^k}{k!}x^k\\
= 0x^0 + 0.003x^1 + 0.036x^2 + 0.101x^3 + 0.156x^4\\
    + 0.175x^5 + 0.161x^6 + 0.128x^7 + 0.092x^8 + \ldots
\end{split}
\end{multline*}

The PGF condition is true (\url{http://tinyurl.com/gnemae8}):

\begin{multline*}
\begin{split}
P(1)\\
= \sum_{k=0}^{\infty}\frac{e^{-5}5^k}{k!}\\
= 0 + 0.003 + 0.036 + 0.101 + 0.156 + 0.175\\
    + 0.161 + 0.128 + 0.092 + \ldots\\
= 1
\end{split}
\end{multline*}

Generally, if you plug in 1 into a generating function some dark magic happens and you suddenly can extract some information.

``Deriving a PGF yields its \emph{moments}'': The first derivation or moment is the expectation value of the PGF. I do not know about other moments. For a PGF with a Poisson Distribution:

\begin{align*}
  P(x) &= \sum_{k=0}^{\infty}\frac{e^{-\lambda}\lambda^k}{k!}x^k = e^{-\lambda}e^{\lambda x}\\
  P'(x) &= \lambda e^{-\lambda}e^{\lambda x}\\
  P''(x) &= \lambda^2 e^{-\lambda}e^{\lambda x}
\end{align*}

\begin{align*}
  P(1) &= \sum_{k=0}^{\infty}\frac{e^{-\lambda}\lambda^k}{k!}x^k = e^{-\lambda}e^{\lambda} = 1\\
  P'(1) &= \lambda e^{-\lambda}e^{\lambda} = \lambda\\
  P''(1) &= \lambda^2 e^{-\lambda}e^{\lambda} = \lambda^2
\end{align*}

Thus the expectation value is $E(K) = \lambda$. We can also calculate the variance\footnote{The proof for this formula is given here as equation 6.3: \url{https://www.cl.cam.ac.uk/teaching/0708/Probabilty/prob06.pdf}}:

\begin{equation*}
\begin{split}
  V(K) &= P''(1) + P'(1) - P'(1)^2\\
       &= \lambda^2 + \lambda - \lambda^2\\
       &= \lambda
\end{split}
\end{equation*}

### 2016-08-24 paper/paper.tex
Explain the cascade windows figure

@@
 
-$
+$$
 f(\phi) =
@@
   \end{cases}
-$
+$$
 
@@
 
+Through some generating functions black magic Watts expresses this cascade condition analytically. A cascade is possible if:
+
+\begin{equation}
+  G_0''(1) = \sum_{k=0}^\infty k (k-1) \rho_k p_k > z
+\end{equation}
+
+Let's break that down:
+
+\begin{itemize}
+  \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
+  \item $k (k-1)$ Nevermind that. These are remainders of the generating functions black magic.
+  \item $\rho_k$ The propability that a node with degree k is vulerable (according to a propability distribution)
+  \item $p_k$ The propability that a node has the threshold $k$ (according to a propability distribution)
+\end{itemize}
+
+In summary, for given propability distributions for both node degree and node threshold, the cascade condition inequation tells us if a vulnerable cluster percolates the network, meaning that global cascades are possible.
+
+To illustrate this, let's choose those distributions and see what happens.
+We'll construct a uniform graph with a homogenous threshold.
+Uniform graphs have a poisson degree distribution $p_k = \frac{e^{-z}z^k}{k!}$ with $z$ being the mean (the peak) of the distribution.
+The fixed threshold is easily modeled: The propability for a node being vulnerable is $\rho_k = P(\phi \leq \frac{1}{k})$, but since $\phi$ (the threshold) in this case is fixed, we just need to use $1$ for $\phi \leq \frac{1}{k}$ and $0$ for $\phi > \frac{1}{k}$ (and $1$ for $k = 0$).
+
+For instance, let's see if cascades are possible for a fixed threshold $\phi = 0.2$ and a poisson-distributed degree with mean $z = 2$:
+
+\begin{table}[h!]
+\centering
+\caption{Uniform graph with $\phi = 0.2$ and $z = 2$}
+\label{lolol}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+\hline
+$k$                       & 0     & 1      & 2     & 3      & 4      & 5      & 6     & \ldots\\ \hline
+$\rho_k$                  & 1     & 1      & 1     & 1      & 1      & 1      & 0     & \ldots\\ \hline
+$p_k$                     & .135  & .271   & .271  & .18    & .09    & .036   & .012  & \ldots\\ \hline
+$k (k-1) \rho_k p_k$  & 0     & 0      & .541  & 1.083  & 1.083  & 0.722  & 0     & \ldots\\ \hline
+\end{tabular}
+\end{table}
+
+The sum of the last row is $\sum_{k=0}^\infty k (k-1) \rho_k p_k = 3.428$, which is greater than $z = 2$, so cascades are possible in this case.
+
+To put this in contrast, let's examine the case of $\phi = 0.2$ and $z = 10$:
+
+\begin{table}[h!]
+\centering
+\caption{Uniform graph with $\phi = 0.2$ and $z = 8$}
+\label{lolol}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+\hline
+$k$                       & 0  & 1     & 2     & 3     & 4     & 5      & 6     & \ldots\\ \hline
+$\rho_k$                  & 1  & 1     & 1     & 1     & 1     & 1      & 0     & \ldots\\ \hline
+$p_k$                     & 0  & .003  & .011  & .029  & .057  & .092   & .122  & \ldots\\ \hline
+$k (k-1) \rho_k p_k$  & 0  & 0     & .021  & .172  & .687  & 1.832  & 0     & \ldots\\ \hline
+\end{tabular}
+\end{table}
+
+Here the sum of the last row is $\sum_{k=0}^\infty k (k-1) \rho_k p_k = 2.712$, which is smaller than $z = 8$, so no cascades will occur.
+
+Watts tested this condition for these distributions for $z$ from $20$ to $0$ and $\phi$ from $0.1$ to $0.3$.
+Figure \ref{fig:cascade-window} depicts the results as a phase transition diagram (dashed line).
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.45\textwidth]{img/cascade-regimes.png}
+  \caption{Cascade Window}
+  \label{fig:cascade-window}
+\end{figure}
+
+There are two areas in this diagram: One in which cascades are possible for the combination of $z$ and $\phi$ and one where no cascades are possible.
+It becomes apparent that there are two important transitions or ``boundaries'': One at an average degree $z = 1$ independent of the threshold, and one whith high average degrees and low threshold, with increasing threshold as the average degree decreases.
+
+The dotted line in the diagram is the result of empirical testings where random networks where generated for the same distributions and the two parameters and tested, i.e.
+simulated.
+It is obvious that the calculated and the empirical phase transitions align (with reasonable precision), which validates the cascade condition inequation.
+
 \section{Findings}\label{sec:findings}

### 2016-08-25 paper/paper.tex
Paper is not sufficiently propable

@@
 This means that the graph of the degree distribution for $p_k$ has its peak at 2 and that we would expect that most nodes have 2 neighbors.
-Plugging that into the distribution function tells us that the propability for this case (2 neighbors) is about $27\%$, and the propability for 1 neighbor is $27\%$, $18\%$ for 3 neighbors, $9\%$ for 4 and $3\%$ for 5, and so on.
+Plugging that into the distribution function tells us that the probability for this case (2 neighbors) is about $27\%$, and the probability for 1 neighbor is $27\%$, $18\%$ for 3 neighbors, $9\%$ for 4 and $3\%$ for 5, and so on.
 According to this, a ``realistic'' network for our potential WhatsApp users might have an connection between Alice and Bob, between Bob and Charly, and Charly and Dave, leaving Alice and Dave with each one neighbour, and Bob and Charly with each two neighbors.
@@
 This random network model is equivalent to an Erdős–Rényi-Model with $p = \frac{z}{n}$.
-Networks following the Erdős–Rényi-Model are build by creating $n$ nodes and creating each possible edge with a propability $p$.
+Networks following the Erdős–Rényi-Model are build by creating $n$ nodes and creating each possible edge with a probability $p$.
 This method generates networks which have a small average distances between nodes and a low amount of clustering.
@@
 Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution $f(\phi): [0,1] \rightarrow [0,1]$ which must be normalized such that $\int_0^1 f(\phi) d\phi = 1$, i.e.
-the area beneath the propability function is 1, which means that all distributions must allocate the same total of propabilities.
-This restriction is necessary because we are assigning a propability to mutually exclusive ``events''.
+the area beneath the probability function is 1, which means that all distributions must allocate the same total of probabilities.
+This restriction is necessary because we are assigning a probability to mutually exclusive ``events''.
 Relating to the example, this represents the ``convincability'' of a person.
 
-The integral restriction is more easily understandable in a discrete case. For our WhatsApp example, we define the following discrete propability distribution:
+The integral restriction is more easily understandable in a discrete case. For our WhatsApp example, we define the following discrete probability distribution:
 
@@
 
-This means that the thresholds $0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9$ all have a propability of $10\%$ to be chosen, the threshold $0.5$ has a chance of $20\%$, and 0 and 1 will not be chosen at all.
-In contrast, we could assign a propability of $100\%$ to the threshold 0 and $0\%$ to all other thresholds and would still conform to the integral restriction.
+This means that the thresholds $0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9$ all have a probability of $10\%$ to be chosen, the threshold $0.5$ has a chance of $20\%$, and 0 and 1 will not be chosen at all.
+In contrast, we could assign a probability of $100\%$ to the threshold 0 and $0\%$ to all other thresholds and would still conform to the integral restriction.
 
@@
 
-In the example with Alice and the others, we apply the first propability distribution from above.
-Let's say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the propability is $20\%$), Charly is assigned $\phi_{Charly} = 0.3$ and Dave $\phi_{Dave} = 0.9$.
+In the example with Alice and the others, we apply the first probability distribution from above.
+Let us say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the probability is $20\%$), Charly is assigned $\phi_{Charly} = 0.3$ and Dave $\phi_{Dave} = 0.9$.
 This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it (switch his state to $1$), whereas Charly already switches if only $30\%$ of his neighbors adopt the technology.
@@
 
-A node is vulnerable if its threshold is low enough so that only one of it's neighbors needs to switch state for it to switch state itslef.
+A node is vulnerable if its threshold is low enough so that only one of its neighbors needs to switch state for it to switch state itslef.
 Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''.
@@
 
-Let's break that down:
+Let us break that down:
 
@@
   \item $k (k-1)$ Nevermind that. These are remainders of the generating functions black magic.
-  \item $\rho_k$ The propability that a node with degree k is vulerable (according to a propability distribution)
-  \item $p_k$ The propability that a node has the threshold $k$ (according to a propability distribution)
+  \item $\rho_k$ The probability that a node with degree k is vulerable (according to a probability distribution)
+  \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
 \end{itemize}
 
-In summary, for given propability distributions for both node degree and node threshold, the cascade condition inequation tells us if a vulnerable cluster percolates the network, meaning that global cascades are possible.
+In summary, for given probability distributions for both node degree and node threshold, the cascade condition inequation tells us if a vulnerable cluster percolates the network, meaning that global cascades are possible.
 
-To illustrate this, let's choose those distributions and see what happens.
-We'll construct a uniform graph with a homogenous threshold.
+To illustrate this, let us choose those distributions and see what happens.
+We will construct a uniform graph with a homogenous threshold.
 Uniform graphs have a poisson degree distribution $p_k = \frac{e^{-z}z^k}{k!}$ with $z$ being the mean (the peak) of the distribution.
-The fixed threshold is easily modeled: The propability for a node being vulnerable is $\rho_k = P(\phi \leq \frac{1}{k})$, but since $\phi$ (the threshold) in this case is fixed, we just need to use $1$ for $\phi \leq \frac{1}{k}$ and $0$ for $\phi > \frac{1}{k}$ (and $1$ for $k = 0$).
+The fixed threshold is easily modeled: The probability for a node being vulnerable is $\rho_k = P(\phi \leq \frac{1}{k})$, but since $\phi$ (the threshold) in this case is fixed, we just need to use $1$ for $\phi \leq \frac{1}{k}$ and $0$ for $\phi > \frac{1}{k}$ (and $1$ for $k = 0$).
 
-For instance, let's see if cascades are possible for a fixed threshold $\phi = 0.2$ and a poisson-distributed degree with mean $z = 2$:
+For instance, let us see if cascades are possible for a fixed threshold $\phi = 0.2$ and a poisson-distributed degree with mean $z = 2$. Table \ref{tab:z2} shows the results for that graph.
 
-\begin{table}[h!]
+\begin{table*}[t!]
 \centering
 \caption{Uniform graph with $\phi = 0.2$ and $z = 2$}
-\label{lolol}
+\label{tab:z2}
 \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 
-To put this in contrast, let's examine the case of $\phi = 0.2$ and $z = 10$:
+To put this in contrast, table \ref{tab:z8} examines the case of $\phi = 0.2$ and $z = 10$. FIXME Marco why does the table say $z = 8$ instead?
 
-\begin{table}[h!]
+\begin{table*}
 \centering
 \caption{Uniform graph with $\phi = 0.2$ and $z = 8$}
-\label{lolol}
+\label{tab:z8}
 \begin{tabular}{|l|l|l|l|l|l|l|l|l|}

### 2016-08-25 paper/paper.tex
Add example and pictures

@@
 \usepackage{csquotes}
+\usepackage{hyperref}
 
@@
 
+In section \ref{sec:example}, a walk-through of a simulation of a simple graph is given.
+
 \section{Model}\label{sec:model}
@@
 According to this, a ``realistic'' network for our potential WhatsApp users might have an connection between Alice and Bob, between Bob and Charly, and Charly and Dave, leaving Alice and Dave with each one neighbour, and Bob and Charly with each two neighbors.
+Figure \ref{fig:abcd} shows the graph for this setup.
 
-%TODO: Image
+\begin{figure}[h!]
+    \includegraphics[width=\columnwidth]{img/abcd}
+    \centering
+    \caption{Alice, Bob, Charly and Dave}
+    \label{fig:abcd}
+\end{figure}
 
@@
 \section{Example}\label{sec:example}
+
+While the previous sections dealt with examples on an abstract level, this section walks through a detailed example of the actual model in action.
+
+To keep the example from being overly long, we will use $n = 5$ agents.
+However, we have also built a simulation application\footnote{The application can be found at \url{https://github.com/turbopope/nss/tree/master/simulator}.}, which can be used to view examples in motion, with many more agents than we could fit into this paper.
+
+Figure \ref{fig:model1} shows the initial state of the graph at $t = 0$. Each agent has its threshold set to a randomly chosen value and its state set to $0$.
+
+\begin{figure}[h!]
+    \includegraphics[width=\columnwidth]{../presentation/img/model4}
+    \centering
+    \caption{Initial State at $t = 0$}
+    \label{fig:model1}
+\end{figure}
+
+In this configuration, nothing actually occurs yet however, since all states are $0$.
+All agents do periodically check their neighbors and calculate if they should change their own state, but of course this always results in no change.
+To actually begin the simulation proper, we change the state of one node to $1$ at a random point in time.
+The new state can be seen in figure \ref{fig:model2}.
+
+\begin{figure}[h!]
+    \includegraphics[width=\columnwidth]{../presentation/img/model5}
+    \centering
+    \caption{State after the initial impulse}
+    \label{fig:model2}
+\end{figure}
+
+As the simulation keeps going, eventually the neighboring node with $\phi = 0.1$ will inspect its neighbors and notice the change.
+It has $4$ neighbors, of which $1$ is in state $1$.
+That means it compares $\frac{1}{4}$ to its own threshold of $0.1$.
+Since the calculated value is above the threshold, the node will change its own state to $1$.
+The new state of the network can be seen in figure \ref{fig:model3}.
+
+\begin{figure}[h!]
+    \includegraphics[width=\columnwidth]{../presentation/img/model6}
+    \centering
+    \caption{State after the second adoption}
+    \label{fig:model3}
+\end{figure}
+
+There are also examples in which the state of the network does not change.
+For instance, if the node with threshold $\phi = 0.8$ checks its surroundings at this point, it will see that $1$ of its $3$ neighbors is in state $1$.
+However, since $\frac{1}{3}$ is below its own threshold of $0.8$, the node's state remains in state $0$.
+
+Next, we will look at the node with threshold $\phi = 0.5$.
+It has $3$ neighbors, of which $2$ have already changed their state.
+Since $\frac{2}{3} > 0.5$, the node also changes its state and the graph's state looks like in figure \ref{fig:model4}.
+
+\begin{figure}[h!]
+    \includegraphics[width=\columnwidth]{../presentation/img/model7}
+    \centering
+    \caption{State after the third adoption}
+    \label{fig:model4}
+\end{figure}
+
+As should be obvious by now, the final two nodes will also change their state at this point.
+First the node with $\phi = 0.5$ and finally the node with $\phi = 0.8$.
+At that point, the entire network is in a stable, unchanging state, as can be seen in figure \ref{fig:model5}.
+Since the entire network has changed its state to a uniform $1$, the cascade successfully worked its way from a single impulse to covering the entire network.
+
+\begin{figure}[h!]
+    \includegraphics[width=\columnwidth]{../presentation/img/model9}
+    \centering
+    \caption{Final state -- successful cascade}
+    \label{fig:model5}
+\end{figure}
+
+Different outcomes could have been possible as well, if a different node were chosen for the initial impulse.
+For instance, if the agent with $\phi = 0.1$ had been chosen, none of its neighbors would have had a low enough threshold to change their state at all.
+In that case, the system would have also entered a stable state, but the cascade would have failed to progress through the network.
 

### 2016-08-25 paper/paper.tex
Complete threats to validity

@@
 All agents do periodically check their neighbors and calculate if they should change their own state, but of course this always results in no change.
-To actually begin the simulation proper, we change the state of one node to $1$ at a random point in time.
+To actually begin the simulation proper, we must create the initial impulse.
+That is, we change the state of one node to $1$ at a random point in time.
+In this case, we have chosen the node with threshold $\phi = 1$.
 The new state can be seen in figure \ref{fig:model2}.
@@
 
-TODO: bimodality with one sample
+The bimodality mentioned in \ref{sec:findings} does not have a significant sample size.
+In fact, there is only a single example of a large example occurring.
+Calling the distribution bimodal due to a single result like that may be a stretch.
+Instead, more experiments should have been conducted to either rule the sample out as a fluke or confirm bimodality through more large samples appearing.
 
-Finally, the paper itself does not have a section on threats to validity. TODO: yo dawg I heard you like to write papers so I'll cite a paper about writing papers so you can read while you write
+Finally, the paper itself does not have a section on threats to validity, despite it being recommended for research design\cite{yodawg}.
 

### 2016-08-25 paper/paper.tex
Clarify cascade condition

@@
 
+That is, a successful cascade is only possible, if the graph's largest connected cluster of agents changes its state to $1$.
+This is only a necessary condition however: if the cascade condition is not fulfilled, a successful cascade is impossible, but a fulfilled cascade condition does not guarantee a successful cascade.
+
 A node is vulnerable if its threshold is low enough so that only one of its neighbors needs to switch state for it to switch state itslef.

### 2016-08-25 paper/paper.tex
Describe what a successful cascade is

@@
 Dave has two neighbors, Bob and Dave, but only needs $30\%$ to switch, so it suffices if either Bob or Dave switch (that would be $50\%$ of his neighbors).
+
+The model is then simulated over time until a steady state is reached.
+That is, the point where the entire system is stable and no agent will ever change its state again.
+The case of a steady state is easily verifiable: if all agents have observed their neighbors at least once since the last time any agent changed its state, then further observations will always lead to the same repeated result of no agent changing its state anymore.
+At this point, the simulation is finished.
+
+After the simulation is done, there can be two results: either the experiment was successful and a global cascade has occurred, or the experiment has failed and the cascade was too small to be considered global.
+
+What exactly constitutes as a successful global cascade is defined by $\frac{\textmd{Number of agents}}{\textmd{Agents in state } 1} \geq T$, where $T \in [0, 1]$ is some arbitrarily chosen threshold value.
+For example, $T = 1$ would require every last agent to have changed its state to $1$, which is difficult to achieve in a large random graph.
+A value like $T = 0.9$ would only require a 90\% majority, but still intuitively result in a cascade that was ``sufficiently global''.
 

### 2016-08-25 paper/paper.tex
Original graph do not steal
FIX ME
Talk about casacade sizes a bit

@@
 
-To put this in contrast, table \ref{tab:z8} examines the case of $\phi = 0.2$ and $z = 10$. FIXME Marco why does the table say $z = 8$ instead?
+To put this in contrast, table \ref{tab:z8} examines the case of $\phi = 0.2$ and $z = 8$.
 
@@
   \includegraphics[width=0.45\textwidth]{img/cascade-regimes.png}
-  \caption{Cascade Window}
+  \caption{Cascade Window, image from \cite{simplemodel}}
   \label{fig:cascade-window}
@@
 \section{Findings}\label{sec:findings}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=\columnwidth]{img/cascade-size}
+  \caption{Cascade Size, image from \cite{simplemodel}. $n = 1000$, squares and solid line use $z = 6.14$, circles and dashed line use $z = 1.05$.}
+  \label{fig:cascade-size}
+\end{figure}
+
+Figure \ref{fig:cascade-size} shows the cumulative distribution of the cascade sizes. The size of a cascade is measured in terms of the ratio between agents in state $1$ to the total number of agents.
+
+At the lower boundary of the cascade window, with $z = 1.05$, the curve resembels a power law distribution (note the logarithmic axes).
+This distribution is very similar to avalances in self-organized criticality models (TODO $wat$).
+This distribution can be explained by most nodes being vulnerable given the low value of $z$, so cascades can spread to neighbors very easily.
+The constraining factor is the connectivity of the network, that is, missing connections inhibit the cascade's progressions, not a high convincability threshold of agents.
+
+On the other hand, the upper boundary behaves the opposite.
+With $z = 6.14$, the limiting factor is the large amounts of neighbors and the resulting difficulty in overcoming an individual node's threshold.
+Connectivity in turn is not a problem anymore, since the large amount of neighbors also gives the graph a high degree of connectivity.
+This leads to the distribution being very bottom-heavy, with most of the cascades failing at an early stage, since only a small amount of surrounding vulnerable agents can be convinced to switch their state.
+In the rare case (really just one case, see section \ref{sec:threats}) that the cascade actually manages to infect the largest vulnerable cluster, a large global cascade that converts a majority of agents is likely.
+This leads to a bimodal distribution, i.e.
+it peaks at low values, is reduced to zero in the middle and then (sort of) peaks again at large values.
 

### 2016-08-25 paper/paper.tex
Introduce the cross section graphs

--- 2016-08-25 paper/paper.tex
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{img/cascade-regimes.png}
-  \caption{Cascade Window}
+  \includegraphics[width=0.45\textwidth]{img/cascade-regimes-with-cross-section.png}
+  \caption{Cascade Window, image from \cite{simplemodel}}
   \label{fig:cascade-window}
@@
 It is obvious that the calculated and the empirical phase transitions align (with reasonable precision), which validates the cascade condition inequation.
+
+The cascade window diagram is limited to a binary statement wether cascades are possible.
+To gain further insight on the the nature of cascades inside the window, Watts examined ``cross section'' of the window for $\phi=0.18$ (marked in firgure \ref{fig:cascade-window} with by the densely stroked line at $\phi=0.18$), consisting of serveral measurements.
+They are depicted in figure \ref{fig:cross-section}.
+The upper graph (a) maps from $z$ to the amount of steps required for the cascade to occur.
+The lower figure (b) maps from $z$ to various percentages.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.45\textwidth]{img/cross-section.png}
+  \caption{Cross section of the cascade window at $\phi=0.18$, image from \cite{simplemodel}}
+  \label{fig:cross-section}
+\end{figure}
+
+There are 6 graphs here:
+
+\begin{itemize}
+  \item \textbf{Solid Circles \& Solid Line} -- These are optically very hard to distinguish from another, as they are virtually equal.
+They form the ``upper graph'' in the figure.
+The former shows the average size of global cascades and the latter shows the (analytical) size of the largest connected component, both as a fraction of the whole network.
+  \item \textbf{Open Circles} -- Frequency of global cascades. Forms the ``middle graph''.
+  \item \textbf{Short Dashes} -- Fractional (to the size of the network) size of the extended vulnerable cluster.
+The extended vulnerable cluster comprises the vulnerable cluster plus it's direct neighbors.
+Forms the ``middle graph''.
+  \item \textbf{Long Dashes} -- The fractional (to the size of the network) size of the vulnerable cluster according to an analytical formula derived by Watts in the text. Forms the ``lower graph''.
+  \item \textbf{Crosses} -- The fractional (to the size of the network) size of the vulnerable cluster, empirically determined by simulation. Forms the ``lower graph''.
+\end{itemize}
+
+Refer to section \ref{sec:findings} for Watts' interpretation of these graphs.
 

### 2016-08-25 paper/paper.tex

@@
 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=\columnwidth]{img/cascade-size}
+  \caption{Cascade Size, image from \cite{simplemodel}. $n = 1000$, squares and solid line use $z = 6.14$, circles and dashed line use $z = 1.05$.}
+  \label{fig:cascade-size}
+\end{figure}
+
+Figure \ref{fig:cascade-size} shows the cumulative distribution of the cascade sizes. The size of a cascade is measured in terms of the ratio between agents in state $1$ to the total number of agents.
+
+At the lower boundary of the cascade window, with $z = 1.05$, the curve resembels a power law distribution (note the logarithmic axes).
+This distribution is very similar to avalances in self-organized criticality models (TODO $wat$).
+This distribution can be explained by most nodes being vulnerable given the low value of $z$, so cascades can spread to neighbors very easily.
+The constraining factor is the connectivity of the network, that is, missing connections inhibit the cascade's progressions, not a high convincability threshold of agents.
+
+On the other hand, the upper boundary behaves the opposite.
+With $z = 6.14$, the limiting factor is the large amounts of neighbors and the resulting difficulty in overcoming an individual node's threshold.
+Connectivity in turn is not a problem anymore, since the large amount of neighbors also gives the graph a high degree of connectivity.
+This leads to the distribution being very bottom-heavy, with most of the cascades failing at an early stage, since only a small amount of surrounding vulnerable agents can be convinced to switch their state.
+In the rare case (really just one case, see section \ref{sec:threats}) that the cascade actually manages to infect the largest vulnerable cluster, a large global cascade that converts a majority of agents is likely.
+This leads to a bimodal distribution, i.e.
+it peaks at low values, is reduced to zero in the middle and then (sort of) peaks again at large values.
+
 \section{Threats to Validity}\label{sec:threats}

### 2016-08-25 paper/paper.tex
Tease readers about the explanation to the cumulative distributions graph
Interpret Watts' figure 2

@@
 Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''.
-A vulerable cluster is a connected set of nodes that all switch state if a contained ``early adopter'' adjacent to an ``innovator'' switches its state.
+A vulerable cluster is a connected set of nodes that are ``early adopters'' (that are vulnerable) adjacent to an ``innovator''.
 This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.
@@
 
+Further insights on the cascade window can be gained by examining the size of cascades around its boundaries.
+Figure \ref{fig:cascade-size} shows the cumulative distribution of the cascade sizes.
+The size of a cascade is measured in terms of the ratio between agents in state $1$ to the total number of agents.
+The examinded section of the window is the same as in figure \ref{fig:cross-section}.
+See \ref{sec:findings} for Watts' interpretation of this graph.
+
 \section{Findings}\label{sec:findings}
+
+In the above section \ref{fig:cross-section} was introduced as a means to compare the properties of the cascade window for a given threshold. Watts' interpretation of the results is as follows:
+
+There is an obvious relation of the frequency of global cascades (open circles, in the middle) to the relative size of the vulnerable cluster (long dashes and crosses, the lower two graphs).
+They are roughly proportional, but the size of the cluster ``underestimates'' the cascade frequency.
+The given explanation for this is, that agents directly adjacent do the vulnerable cluster (who are themselves not vulnerable) can still trigger further cascades or promote the expansion of a cascade in the latter state of the cascade when most of it's vulnerable neighbors have been switched.
+This explanation is validated by examining the size of the extended vulnerable cluster, which comprises the vulnerable cluster plus its immediate (stable) neighbor nodes.
+And indeed the plot for the extended vulnerable cluster (short dashes, in the middle) is virtually equal to the cascade frequency, thus validating the explanation.
+
+The average size of global cascades (solid line and solid circles, the upper graphs) is obviously not related to the size of the vulnerable cluster or the extended vulnerable cluster, since it does not decline with decreasing sizes for greater values of $z$.
+It is only governed by the $z$, i.e.
+the connectivity of the whole network.
+The raltionship between connectivity and cascade size is further examined below, using figure \ref{fig:cascade-size}.
+The intuition that with decresing size of the vulnerable cluster (to which the cascade is limited) the size of cascades should also decrease is false.
+Although unable to give a defititive explanation, Watts tries to explain this phenomenon: In the later stages of the cascade, the cascade has switched a lot of vulnerable nodes to $1$.
+In this situation it is possible that stable nodes, i.e.
+nodes that need more than one neighbor switching to switch themselves, have multiple switched adjacent vulnerable nodes and now do switch.
+This process could repeat itself until the entire connected component to which the vlunerable cluster belongs might be switched.
+Watts did not investigate in this paper if this phenomenon only occurs in the examinded class of random graphs or if it also appears in other random graphs.
 

### 2016-08-25 paper/paper.tex
Add Related Work section

@@
 
+\section{Related Work}
+
+The mathematical basis for the calculations in section \ref{sec:cascade-condition} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition).
+Generating functions are a convenient tool to express series of numbers in a concise fashion.
+Applied to propability distributions, they allow for a convenient examination of that distribution.
+
+An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts in his paper below).
+
+A slightly different and more basic version of the approach to finding an analytical cascade condition is described by Watts and his co-authors in \cite{newman2001random}.
+They use generating functions to express the degree distribution of arbitrary networks and then analyze for component sizes, average component sizes and the phase transition between going from a largely unconnected network to a network that is mostly one single connected component (the ``giant component'', in terms of the paper).
+One can easily see, although this is only a very high level description of the paper's contents, that there are striking parallels to this paper about network cascades.
+They also go a bit further and analyze for the asymptotic form of the cluster size distribution, the number of neighbors and the average path length.
+
 \section{Threats to Validity}\label{sec:threats}

### 2016-08-25 paper/paper.tex
Alter the ets

@@
 
-An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts in his paper below).
+An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts et. al. in his paper below).
 

### 2016-08-25 paper/paper.tex
Give them another one for motivation

@@
 
-% TODO: At least one more example
+To give another example, the model of network cascades can help to explain how some cultural artifacts like books or movies can emerge out of obscurity, while other artifacts never receive the attention of the general public, although being qualitatively comparable on an objective level.
+The basic assumption here is that the audience will make the decision of wether to give an artifact (a product) attention based on their observation of their social neighbors, rather than on their personal information.
+``If all other people in my group of friends are reading a book then I too should read that book''.
+
+Research in this area is in particular interest for marketing, where understanding the dynamics of the target marked network can lead to important insights on how to promote a product and hopefully encourage a cascade in said network, resulting in favorable sales figures.
 

### 2016-08-25 paper/paper.tex
Do some minor improvements

@@
 
-\section{Cascade Condition}\label{sec:section}
+\section{Analysis of the Model}\label{sec:analysis}
 
@@
   \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
+  \item $G_0''(1)$ Treat this as an alias for the sum term.
+It is actually the solution for $x = 1$ of the second derivative of the generating function for the distribution of vulnerable nodes (which is $G_0(x) = \sum_k \rho_kp_kx^k$; the derivative-relationship is clearly visible)
 \end{itemize}
@@
 
-The mathematical basis for the calculations in section \ref{sec:cascade-condition} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition).
+The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition).
 Generating functions are a convenient tool to express series of numbers in a concise fashion.

### 2016-08-25 paper/paper.tex
Add section for summary
Write a summary

@@
 
+% TODO: Explanation of the cascade window boundaries/regimes
+
 There is an obvious relation of the frequency of global cascades (open circles, in the middle) to the relative size of the vulnerable cluster (long dashes and crosses, the lower two graphs).
@@
 
+\section{Summary}\label{sec:summary}
+
+In his paper, Watts introduced a network-theoretical model to explain the occurrance of network cascades.
+The model is analyzed analytically and empirically and at least for some graph classes conditions for cascades are found.
+There are two so called regimes of these conditions: One where average degree of the network is low and the threshold is unimportant.
+Here the cascade size exhibits a power law distribution.
+As the average degree increases, the threshold under the fraction of neighboring activated nodes must lie must decrease in order to retain vulnerability, and thus becomes the limiting factor.
+Here the distribution of the cascade size is bimodal, with many small cascades and some very large cascades.
+Also further effects of network properties are examined.
+
+We motivated this model and explained it in detail.
+The mathematical details of the analysis have been intentionally left out, but its general approach was shown with more complementary explanations to the derived figures in Watts' paper.
+Finally, Watts' findings and their interpretation have been reported on.
+
 \bibliographystyle{abbrv}

### 2016-08-26 paper/paper.tex
Remove a todo that I did before
Fix some more spelling

@@
 
-% TODO: Explanation of the cascade window boundaries/regimes
-
 There is an obvious relation of the frequency of global cascades (open circles, in the middle) to the relative size of the vulnerable cluster (long dashes and crosses, the lower two graphs).
@@
 
-The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition).
+The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by generating functions (hence the name $G_0''(1)$ for the condition).
 Generating functions are a convenient tool to express series of numbers in a concise fashion.
-Applied to propability distributions, they allow for a convenient examination of that distribution.
+Applied to probability distributions, they allow for a convenient examination of that distribution.
 

### 2016-08-26 paper/paper.tex
Add the final two graphs to findings section

@@
 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=\columnwidth]{img/heterogenity}
+  \caption{Effect of heterogenity on cascade size, image from \cite{simplemodel}. The $\phi$ are normally distribute width a standard derivation of $\sigma$.}
+  \label{fig:heterogenity}
+\end{figure}
+
+Similarly distributed results can be observed in networks that vary in their distribution of $\phi$ and $p_k$, but the exact results differ in quantity.
+Figure \ref{fig:heterogenity} shows that increasing the variation of thresholds in the network also increases the likelihood of cascades.
+Using identical, homogenous thresholds for all agents yields the most stable system, while increasing the derivation and giving the nodes differing thresholds consistently decreases this stability, enabling more successful cascades.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=\columnwidth]{img/dunnolol}
+  \caption{A confusing graph, image from \cite{simplemodel}.}
+  \label{fig:heterogenity}
+\end{figure}
+
 \section{Related Work}

### 2016-08-26 paper/paper.tex
Add section foreshadowing bit

@@
 
-Section \ref{sec:model} presents a simple network cascade model as laid out by Watts\cite{simplemodel}.
+Section \ref{sec:model} presents a simple network cascade model as laid out by Watts\cite{simplemodel}. This is followed by a walk-through if a full simulation in section \ref{sec:example}.
 
-In section \ref{sec:example}, a walk-through of a simulation of a simple graph is given.
+In section \ref{sec:analysis}, the model is analyzed in regards to the possibility condition of global cascades. Section \ref{sec:findings} inspects the further results from Watts' research.
+
+Section \ref{sec:threats} lists limitations and threats to validity of the original paper by Watts, which we discovered while compiling this work.
+
+Finally, section \ref{sec:related-work} shows related work and section \ref{sec:summary} concludes the seminar paper's results.
 
@@
 
-\section{Related Work}
-
-The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by generating functions (hence the name $G_0''(1)$ for the condition).
-Generating functions are a convenient tool to express series of numbers in a concise fashion.
-Applied to probability distributions, they allow for a convenient examination of that distribution.
-
-An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts et. al. in his paper below).
-
-A slightly different and more basic version of the approach to finding an analytical cascade condition is described by Watts and his co-authors in \cite{newman2001random}.
-They use generating functions to express the degree distribution of arbitrary networks and then analyze for component sizes, average component sizes and the phase transition between going from a largely unconnected network to a network that is mostly one single connected component (the ``giant component'', in terms of the paper).
-One can easily see, although this is only a very high level description of the paper's contents, that there are striking parallels to this paper about network cascades.
-They also go a bit further and analyze for the asymptotic form of the cluster size distribution, the number of neighbors and the average path length.
-
 \section{Threats to Validity}\label{sec:threats}
@@
 
-\section{Summary}\label{sec:summary}
+\section{Related Work}\label{sec:related-work}
+
+The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by generating functions (hence the name $G_0''(1)$ for the condition).
+Generating functions are a convenient tool to express series of numbers in a concise fashion.
+Applied to probability distributions, they allow for a convenient examination of that distribution.
+
+An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts et. al. in his paper below).
+
+A slightly different and more basic version of the approach to finding an analytical cascade condition is described by Watts and his co-authors in \cite{newman2001random}.
+They use generating functions to express the degree distribution of arbitrary networks and then analyze for component sizes, average component sizes and the phase transition between going from a largely unconnected network to a network that is mostly one single connected component (the ``giant component'', in terms of the paper).
+One can easily see, although this is only a very high level description of the paper's contents, that there are striking parallels to this paper about network cascades.
+They also go a bit further and analyze for the asymptotic form of the cluster size distribution, the number of neighbors and the average path length.
+
+\section{Conclusion}\label{sec:summary}
 

### 2016-08-26 paper/paper.tex
Explain confusing graph too

@@
   \includegraphics[width=\columnwidth]{img/dunnolol}
-  \caption{A confusing graph, image from \cite{simplemodel}.}
-  \label{fig:heterogenity}
+  \caption{Effect of connectivity, image from \cite{simplemodel}. The solid line uses a Poisson distribution, while the dashed line uses a power law distribution of connections.}
+  \label{fig:dunnolol}
 \end{figure}
+
+The same goes for a change in connectivity distribution, as can be seen in figure \ref{fig:dunnolol}.
+A uniform Poisson distribution has a higher rate of cascades than a power-law distributed graph.
+This can be explained by the compound effects from before.
+In a power law distribution, there are pockets of low connectivity, where it impedes the progress of the cascade.
+There are also pockets of high connectivity, leading to nodes with many neighbors, which makes reaching their neighbor threshold difficult.
 

### 2016-08-26 paper/paper.tex
Fix all the spelling

@@
 To give another example, the model of network cascades can help to explain how some cultural artifacts like books or movies can emerge out of obscurity, while other artifacts never receive the attention of the general public, although being qualitatively comparable on an objective level.
-The basic assumption here is that the audience will make the decision of wether to give an artifact (a product) attention based on their observation of their social neighbors, rather than on their personal information.
+The basic assumption here is that the audience will make the decision of whether to give an artifact (a product) attention based on their observation of their social neighbors, rather than on their personal information.
 ``If all other people in my group of friends are reading a book then I too should read that book''.
@@
 
-Relating this to the example, this might mean that Alice, Bob, Charly and Dave are ``agents'' who are faced with the decision if they should jump on the WhatsApp bandwagon and are thus each represented as a node in the network.
+Relating this to the example, this might mean that Alice, Bob, Charley and Dave are ``agents'' who are faced with the decision if they should jump on the WhatsApp bandwagon and are thus each represented as a node in the network.
 
@@
 These edges represent the neighbors that each node observes, or in the example's terms, the person's friends.
-$p_k$ is poisson-distributed: $p_k = \frac{e^{-z}z^k}{k!}$, with $z = \left<k\right>$ being the expectation-value of $p_k$ (the average degree).
+$p_k$ is Poisson-distributed: $p_k = \frac{e^{-z}z^k}{k!}$, with $z = \left<k\right>$ being the expectation-value of $p_k$ (the average degree).
 
@@
 Plugging that into the distribution function tells us that the probability for this case (2 neighbors) is about $27\%$, and the probability for 1 neighbor is $27\%$, $18\%$ for 3 neighbors, $9\%$ for 4 and $3\%$ for 5, and so on.
-According to this, a ``realistic'' network for our potential WhatsApp users might have an connection between Alice and Bob, between Bob and Charly, and Charly and Dave, leaving Alice and Dave with each one neighbour, and Bob and Charly with each two neighbors.
+According to this, a ``realistic'' network for our potential WhatsApp users might have an connection between Alice and Bob, between Bob and Charley, and Charley and Dave, leaving Alice and Dave with each one neighbour, and Bob and Charley with each two neighbors.
 Figure \ref{fig:abcd} shows the graph for this setup.
@@
     \centering
-    \caption{Alice, Bob, Charly and Dave}
+    \caption{Alice, Bob, Charley and Dave}
     \label{fig:abcd}
@@
 
-This random network model is equivalent to an Erdős–Rényi-Model with $p = \frac{z}{n}$.
-Networks following the Erdős–Rényi-Model are build by creating $n$ nodes and creating each possible edge with a probability $p$.
+This random network model is equivalent to an Erdős-Rényi-Model with $p = \frac{z}{n}$.
+Networks following the Erdős-Rényi-Model are build by creating $n$ nodes and creating each possible edge with a probability $p$.
 This method generates networks which have a small average distances between nodes and a low amount of clustering.
@@
 With $z = 2$ $p$ is $\frac{2}{4} = 0.5$, so we would expect half of all possible edges to exist.
-There are 6 possible edges in the network (this is excluding edges from a node to itself), and we chose to create 3, so our example indeed conforms perfectly to the Erdős–Rényi-Model.
+There are 6 possible edges in the network (this is excluding edges from a node to itself), and we chose to create 3, so our example indeed conforms perfectly to the Erdős-Rényi-Model.
 
@@
 In the example with Alice and the others, we apply the first probability distribution from above.
-Let us say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the probability is $20\%$), Charly is assigned $\phi_{Charly} = 0.3$ and Dave $\phi_{Dave} = 0.9$.
-This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it (switch his state to $1$), whereas Charly already switches if only $30\%$ of his neighbors adopt the technology.
-Since Dave has only 1 neighbor, Charly, he switches as soon as Charly switches (in this case, $100\%$ of his neighbors would have switched).
+Let us say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the probability is $20\%$), Charley is assigned $\phi_{Charley} = 0.3$ and Dave $\phi_{Dave} = 0.9$.
+This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it (switch his state to $1$), whereas Charley already switches if only $30\%$ of his neighbors adopt the technology.
+Since Dave has only 1 neighbor, Charley, he switches as soon as Charley switches (in this case, $100\%$ of his neighbors would have switched).
 Dave has two neighbors, Bob and Dave, but only needs $30\%$ to switch, so it suffices if either Bob or Dave switch (that would be $50\%$ of his neighbors).
@@
 
-A node is vulnerable if its threshold is low enough so that only one of its neighbors needs to switch state for it to switch state itslef.
-Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''.
-A vulerable cluster is a connected set of nodes that are ``early adopters'' (that are vulnerable) adjacent to an ``innovator''.
+A node is vulnerable if its threshold is low enough so that only one of its neighbors needs to switch state for it to switch state itself.
+Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed being an ``innovator''.
+A vulnerable cluster is a connected set of nodes that are ``early adopters'' (that are vulnerable) adjacent to an ``innovator''.
 This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.
@@
   \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
-  \item $k (k-1)$ Nevermind that. These are remainders of the generating functions black magic.
-  \item $\rho_k$ The probability that a node with degree k is vulerable (according to a probability distribution)
+  \item $k (k-1)$ Never mind that. These are remainders of the generating functions black magic.
+  \item $\rho_k$ The probability that a node with degree $k$ is vulnerable (according to a probability distribution)
   \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
@@
 To illustrate this, let us choose those distributions and see what happens.
-We will construct a uniform graph with a homogenous threshold.
-Uniform graphs have a poisson degree distribution $p_k = \frac{e^{-z}z^k}{k!}$ with $z$ being the mean (the peak) of the distribution.
+We will construct a uniform graph with a homogeneous threshold.
+Uniform graphs have a Poisson degree distribution $p_k = \frac{e^{-z}z^k}{k!}$ with $z$ being the mean (the peak) of the distribution.
 The fixed threshold is easily modeled: The probability for a node being vulnerable is $\rho_k = P(\phi \leq \frac{1}{k})$, but since $\phi$ (the threshold) in this case is fixed, we just need to use $1$ for $\phi \leq \frac{1}{k}$ and $0$ for $\phi > \frac{1}{k}$ (and $1$ for $k = 0$).
 
-For instance, let us see if cascades are possible for a fixed threshold $\phi = 0.2$ and a poisson-distributed degree with mean $z = 2$. Table \ref{tab:z2} shows the results for that graph.
+For instance, let us see if cascades are possible for a fixed threshold $\phi = 0.2$ and a Poisson-distributed degree with mean $z = 2$. Table \ref{tab:z2} shows the results for that graph.
 
@@
 There are two areas in this diagram: One in which cascades are possible for the combination of $z$ and $\phi$ and one where no cascades are possible.
-It becomes apparent that there are two important transitions or ``boundaries'': One at an average degree $z = 1$ independent of the threshold, and one whith high average degrees and low threshold, with increasing threshold as the average degree decreases.
+It becomes apparent that there are two important transitions or ``boundaries'': One at an average degree $z = 1$ independent of the threshold, and one with high average degrees and low threshold, with increasing threshold as the average degree decreases.
 
@@
 
-The cascade window diagram is limited to a binary statement wether cascades are possible.
-To gain further insight on the the nature of cascades inside the window, Watts examined ``cross section'' of the window for $\phi=0.18$ (marked in firgure \ref{fig:cascade-window} with by the densely stroked line at $\phi=0.18$), consisting of serveral measurements.
+The cascade window diagram is limited to a binary statement whether cascades are possible.
+To gain further insight on  the nature of cascades inside the window, Watts examined ``cross section'' of the window for $\phi=0.18$ (marked in figure \ref{fig:cascade-window} with by the densely stroked line at $\phi=0.18$), consisting of several measurements.
 They are depicted in figure \ref{fig:cross-section}.
@@
 The size of a cascade is measured in terms of the ratio between agents in state $1$ to the total number of agents.
-The examinded section of the window is the same as in figure \ref{fig:cross-section}.
+The examined section of the window is the same as in figure \ref{fig:cross-section}.
 See \ref{sec:findings} for Watts' interpretation of this graph.
@@
 the connectivity of the whole network.
-The raltionship between connectivity and cascade size is further examined below, using figure \ref{fig:cascade-size}.
-The intuition that with decresing size of the vulnerable cluster (to which the cascade is limited) the size of cascades should also decrease is false.
-Although unable to give a defititive explanation, Watts tries to explain this phenomenon: In the later stages of the cascade, the cascade has switched a lot of vulnerable nodes to $1$.
+The relationship between connectivity and cascade size is further examined below, using figure \ref{fig:cascade-size}.
+The intuition that with decreasing size of the vulnerable cluster (to which the cascade is limited) the size of cascades should also decrease is false.
+Although unable to give a definitive explanation, Watts tries to explain this phenomenon: In the later stages of the cascade, the cascade has switched a lot of vulnerable nodes to $1$.
 In this situation it is possible that stable nodes, i.e.
 nodes that need more than one neighbor switching to switch themselves, have multiple switched adjacent vulnerable nodes and now do switch.
-This process could repeat itself until the entire connected component to which the vlunerable cluster belongs might be switched.
-Watts did not investigate in this paper if this phenomenon only occurs in the examinded class of random graphs or if it also appears in other random graphs.
+This process could repeat itself until the entire connected component to which the vulnerable cluster belongs might be switched.
+Watts did not investigate in this paper if this phenomenon only occurs in the examined class of random graphs or if it also appears in other random graphs.
 
@@
 
-At the lower boundary of the cascade window, with $z = 1.05$, the curve resembels a power law distribution (note the logarithmic axes).
-This distribution is very similar to avalances in self-organized criticality models (TODO $wat$).
+At the lower boundary of the cascade window, with $z = 1.05$, the curve resembles a power law distribution (note the logarithmic axes).
+This distribution is very similar to avalanches in self-organized criticality models (TODO $wat$).
 This distribution can be explained by most nodes being vulnerable given the low value of $z$, so cascades can spread to neighbors very easily.
@@
   \includegraphics[width=\columnwidth]{img/heterogenity}
-  \caption{Effect of heterogenity on cascade size, image from \cite{simplemodel}. The $\phi$ are normally distribute width a standard derivation of $\sigma$.}
+  \caption{Effect of heterogeneity on cascade size, image from \cite{simplemodel}. The $\phi$ are normally distribute width a standard derivation of $\sigma$.}
   \label{fig:heterogenity}
@@
 Figure \ref{fig:heterogenity} shows that increasing the variation of thresholds in the network also increases the likelihood of cascades.
-Using identical, homogenous thresholds for all agents yields the most stable system, while increasing the derivation and giving the nodes differing thresholds consistently decreases this stability, enabling more successful cascades.
+Using identical, homogeneous thresholds for all agents yields the most stable system, while increasing the derivation and giving the nodes differing thresholds consistently decreases this stability, enabling more successful cascades.
 
@@
 
-In his paper, Watts introduced a network-theoretical model to explain the occurrance of network cascades.
+In his paper, Watts introduced a network-theoretical model to explain the occurrence of network cascades.
 The model is analyzed analytically and empirically and at least for some graph classes conditions for cascades are found.

### 2016-08-26 paper/paper.tex
Remove criticality thing, Watts reference is broke
Fix introduction to be less cavemany

@@
 
-Since caveman times people have been wondering how the ball gets rolling.
+Many phenomena in society seemingly start from nothing and propagate through people until they reach everyone.
+Examples include popular media, technology use, viral videos and even political activism, such as coups or protest movements: all of them usually start as an idea in the heads of few people and somehow gain popularity by spreading from person to person.
 
@@
 At the lower boundary of the cascade window, with $z = 1.05$, the curve resembles a power law distribution (note the logarithmic axes).
-This distribution is very similar to avalanches in self-organized criticality models (TODO $wat$).
 This distribution can be explained by most nodes being vulnerable given the low value of $z$, so cascades can spread to neighbors very easily.

### 2016-08-26 paper/paper.tex
Change subtitle to something sensible
Add concrete abstract

@@
 \title{Network Cascades}
-\subtitle{WattsApp With Those}
+\subtitle{Watts' Simple Global Cascade Model}
 \author{Marco Brack \and Carsten Hartenfels}
@@
 \begin{abstract}
-Concrete.
+Network cascades can be used to model social phenomena propagation, such as the uptake in use of communication technologies.
+
+The paper ``A simple model of global cascades on random networks'' by Duncan J.
+Watts provides a way to model these kinds of cascades on random graphs.
+From this model, constraint conditions for the success of global cascades can be extracted.
+
+We give an overview of the model combined with high-level, real world examples.
+The mathematical properties and findings of Watts' model are explained in detail.
+We also give the paper a treatment in regards to limitations and threats to validity, which the original does not mention about itself.
 \end{abstract}

### 2016-08-26 paper/paper.tex
Reduce magic

@@
 
-Through some generating functions black magic Watts expresses this cascade condition analytically. A cascade is possible if:
+Through generating functions Watts expresses this cascade condition analytically. A cascade is possible if:
 
@@
   \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
-  \item $k (k-1)$ Never mind that. These are remainders of the generating functions black magic.
+  \item $k (k-1)$ These are remnants from the generating functions and are not directly relevant to the calculation.
   \item $\rho_k$ The probability that a node with degree $k$ is vulnerable (according to a probability distribution)

### 2016-08-26 paper/paper.tex
Fix hyperref box to not spew over the entire page

@@
 
+We have built a simulation application\footnote{The application can be found at \url{https://github.com/turbopope/nss/tree/master/simulator}.}, which can be used to view examples in motion, with many more agents than we could fit into this paper.
+
 To keep the example from being overly long, we will use $n = 5$ agents.
-However, we have also built a simulation application\footnote{The application can be found at \url{https://github.com/turbopope/nss/tree/master/simulator}.}, which can be used to view examples in motion, with many more agents than we could fit into this paper.
-
-Figure \ref{fig:model1} shows the initial state of the graph at $t = 0$. Each agent has its threshold set to a randomly chosen value and its state set to $0$.
+Figure \ref{fig:model1} shows the initial state of the graph at $t = 0$.
+Each agent has its threshold set to a randomly chosen value and its state set to $0$.
 

### 2016-09-22 paper/paper.tex
Incorporate review 1's suggestions

@@
 Then they tell their friends about it, convincing some of them to also begin using the application to communicate.
-Those friends to the same with their own friends, and so on and so forth.
+Those friends do the same with their own friends, and so on and so forth.
 Given a suitably connected social network and a high enough ``convincability'' of its members, the usage will cascade through the entire network and eventually spread to all, or at least most, of its members.
@@
 To give another example, the model of network cascades can help to explain how some cultural artifacts like books or movies can emerge out of obscurity, while other artifacts never receive the attention of the general public, although being qualitatively comparable on an objective level.
-The basic assumption here is that the audience will make the decision of whether to give an artifact (a product) attention based on their observation of their social neighbors, rather than on their personal information.
+The basic assumption here is that the audience will make the decision of whether to give an product or ``artifact'' attention based on their observation of their social neighbors, rather than on their personal information.
 ``If all other people in my group of friends are reading a book then I too should read that book''.
@@
 This means that the graph of the degree distribution for $p_k$ has its peak at 2 and that we would expect that most nodes have 2 neighbors.
-Plugging that into the distribution function tells us that the probability for this case (2 neighbors) is about $27\%$, and the probability for 1 neighbor is $27\%$, $18\%$ for 3 neighbors, $9\%$ for 4 and $3\%$ for 5, and so on.
+Plugging that into the distribution function tells us that the probability for this case of 2 neighbors is about $27\%$, and the probability for 1 neighbor is $27\%$, $18\%$ for 3 neighbors, $9\%$ for 4 and $3\%$ for 5, and so on.
 According to this, a ``realistic'' network for our potential WhatsApp users might have an connection between Alice and Bob, between Bob and Charley, and Charley and Dave, leaving Alice and Dave with each one neighbour, and Bob and Charley with each two neighbors.
@@
 With $z = 2$ $p$ is $\frac{2}{4} = 0.5$, so we would expect half of all possible edges to exist.
-There are 6 possible edges in the network (this is excluding edges from a node to itself), and we chose to create 3, so our example indeed conforms perfectly to the Erdős-Rényi-Model.
+There are 6 possible edges in the network, excluding edges from a node to itself, and we chose to create 3, so our example indeed conforms perfectly to the Erdős-Rényi-Model.
 
@@
 Now the model is simulated over a time $t$, starting with $0$.
-At a random point in time, the state of a single node (the seed) is changed to $1$.
+At a random point in time, the state of a single node, called ``the seed'', is changed to $1$.
 This is analogous to the first person starting to use the application.
@@
 Let us say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the probability is $20\%$), Charley is assigned $\phi_{Charley} = 0.3$ and Dave $\phi_{Dave} = 0.9$.
-This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it (switch his state to $1$), whereas Charley already switches if only $30\%$ of his neighbors adopt the technology.
-Since Dave has only 1 neighbor, Charley, he switches as soon as Charley switches (in this case, $100\%$ of his neighbors would have switched).
-Dave has two neighbors, Bob and Dave, but only needs $30\%$ to switch, so it suffices if either Bob or Dave switch (that would be $50\%$ of his neighbors).
+This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it i.e.
+switch his state to $1$, whereas Charley already switches if only $30\%$ of his neighbors adopt the technology.
+Since Dave has only 1 neighbor, Charley, he switches as soon as Charley switches: In this case, $100\%$ of his neighbors would have switched.
+Dave has two neighbors, Bob and Dave, but only needs $30\%$ to switch, so it suffices if either Bob or Dave switch.
+This would be $50\%$ of his neighbors.
 
@@
 
-What exactly constitutes as a successful global cascade is defined by $\frac{\textmd{Number of agents}}{\textmd{Agents in state } 1} \geq T$, where $T \in [0, 1]$ is some arbitrarily chosen threshold value.
+What exactly constitutes as a successful global cascade is defined by $NumberOfAgents/AgentsInState1 \geq T$, where $T \in [0, 1]$ is some arbitrarily chosen threshold value.
 For example, $T = 1$ would require every last agent to have changed its state to $1$, which is difficult to achieve in a large random graph.
@@
 All agents do periodically check their neighbors and calculate if they should change their own state, but of course this always results in no change.
-To actually begin the simulation proper, we must create the initial impulse.
+To actually begin the simulation properly, we must create the initial impulse.
 That is, we change the state of one node to $1$ at a random point in time.
@@
 
-As should be obvious by now, the final two nodes will also change their state at this point.
+As should be obvious by now, the final two nodes will now also change their state.
 First the node with $\phi = 0.5$ and finally the node with $\phi = 0.8$.
@@
 
-Watts claims that global cascades are only possible if \textquote{the largest vulnerable cluster percolates}. This is called the \emph{cascade condition}.
+Watts claims that global cascades are only possible if \textquote{the largest vulnerable cluster percolates}\cite{simplemodel}. This is called the \emph{cascade condition}.
 
@@
 A vulnerable cluster is a connected set of nodes that are ``early adopters'' (that are vulnerable) adjacent to an ``innovator''.
-This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.
+This cluster must span a sufficiently large portion of the network for the cascade condition to be true.
+``Spanning the network'' is called ``percolating'' int the paper.
+Watts never explicitly states what ``sufficient spanning'' in this case means, unfortunately.
 
@@
 We will construct a uniform graph with a homogeneous threshold.
-Uniform graphs have a Poisson degree distribution $p_k = \frac{e^{-z}z^k}{k!}$ with $z$ being the mean (the peak) of the distribution.
-The fixed threshold is easily modeled: The probability for a node being vulnerable is $\rho_k = P(\phi \leq \frac{1}{k})$, but since $\phi$ (the threshold) in this case is fixed, we just need to use $1$ for $\phi \leq \frac{1}{k}$ and $0$ for $\phi > \frac{1}{k}$ (and $1$ for $k = 0$).
+Uniform graphs have a Poisson degree distribution $p_k = \frac{e^{-z}z^k}{k!}$ with $z$ being the mean of the distribution.
+The fixed threshold is easily modeled: The probability for a node being vulnerable is $\rho_k = P(\phi \leq \frac{1}{k})$, but since the threshold $\phi$ in this case is fixed, we just need to use $1$ for $\phi \leq \frac{1}{k}$ and $0$ for $\phi > \frac{1}{k}$ (and $1$ for $k = 0$).
 
@@
 simulated.
-It is obvious that the calculated and the empirical phase transitions align (with reasonable precision), which validates the cascade condition inequation.
+It is obvious that the calculated and the empirical phase transitions align with reasonable precision, which validates the cascade condition inequation.
 
@@
 
-In the above section \ref{fig:cross-section} was introduced as a means to compare the properties of the cascade window for a given threshold. Watts' interpretation of the results is as follows:
+In the above figure \ref{fig:cross-section} was introduced as a means to compare the properties of the cascade window for a given threshold. Watts' interpretation of the results is as follows:
 
@@
 
-An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts et. al. in his paper below).
+An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology}. Tthis version of the book is referenced by Watts et. al. in his paper below.
 

### 2016-09-22 paper/paper.tex
Incorporate review 2's suggestions

@@
 In this case, we have chosen the node with threshold $\phi = 1$.
-The new state can be seen in figure \ref{fig:model2}.
+The new state can be seen in Figure \ref{fig:model2}.
 
@@
 Since the calculated value is above the threshold, the node will change its own state to $1$.
-The new state of the network can be seen in figure \ref{fig:model3}.
+The new state of the network can be seen in Figure \ref{fig:model3}.
 
@@
 It has $3$ neighbors, of which $2$ have already changed their state.
-Since $\frac{2}{3} > 0.5$, the node also changes its state and the graph's state looks like in figure \ref{fig:model4}.
+Since $\frac{2}{3} > 0.5$, the node also changes its state and the graph's state looks like in Figure \ref{fig:model4}.
 
@@
 First the node with $\phi = 0.5$ and finally the node with $\phi = 0.8$.
-At that point, the entire network is in a stable, unchanging state, as can be seen in figure \ref{fig:model5}.
+At that point, the entire network is in a stable, unchanging state, as can be seen in Figure \ref{fig:model5}.
 Since the entire network has changed its state to a uniform $1$, the cascade successfully worked its way from a single impulse to covering the entire network.
@@
 The cascade window diagram is limited to a binary statement whether cascades are possible.
-To gain further insight on  the nature of cascades inside the window, Watts examined ``cross section'' of the window for $\phi=0.18$ (marked in figure \ref{fig:cascade-window} with by the densely stroked line at $\phi=0.18$), consisting of several measurements.
-They are depicted in figure \ref{fig:cross-section}.
+To gain further insight on  the nature of cascades inside the window, Watts examined ``cross section'' of the window for $\phi=0.18$ (marked in Figure \ref{fig:cascade-window} with by the densely stroked line at $\phi=0.18$), consisting of several measurements.
+They are depicted in Figure \ref{fig:cross-section}.
 The upper graph (a) maps from $z$ to the amount of steps required for the cascade to occur.
@@
 The size of a cascade is measured in terms of the ratio between agents in state $1$ to the total number of agents.
-The examined section of the window is the same as in figure \ref{fig:cross-section}.
+The examined section of the window is the same as in Figure \ref{fig:cross-section}.
 See \ref{sec:findings} for Watts' interpretation of this graph.
@@
 
-In the above figure \ref{fig:cross-section} was introduced as a means to compare the properties of the cascade window for a given threshold. Watts' interpretation of the results is as follows:
+In the above Figure \ref{fig:cross-section} was introduced as a means to compare the properties of the cascade window for a given threshold. Watts' interpretation of the results is as follows:
 
@@
 the connectivity of the whole network.
-The relationship between connectivity and cascade size is further examined below, using figure \ref{fig:cascade-size}.
+The relationship between connectivity and cascade size is further examined below, using Figure \ref{fig:cascade-size}.
 The intuition that with decreasing size of the vulnerable cluster (to which the cascade is limited) the size of cascades should also decrease is false.
@@
 
-The same goes for a change in connectivity distribution, as can be seen in figure \ref{fig:dunnolol}.
+The same goes for a change in connectivity distribution, as can be seen in Figure \ref{fig:dunnolol}.
 A uniform Poisson distribution has a higher rate of cascades than a power-law distributed graph.

### 2016-09-23 paper/paper.tex
Add some more related work

@@
 
-An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology}. Tthis version of the book is referenced by Watts et. al. in his paper below.
+An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology}. This version of the book is referenced by Watts et. al. in his paper below.
 
@@
 
+There also exists an extension to Watt's model for use with temporal networks in \cite{temporal}.
+Those networks add the dimension of time, which means, for instance, links between nodes may only exist at certain points in time.
+This is clearly a useful property for extending Watt's model, where nodes periodically check the state of their neighbors, since it can be modelled in more detail using a temporal network.
+The paper contrasts their approaches with Watt's original model and also tries out a version where thresholds are absolute numbers, rather than relative fractions of neighbors.
+
+\newpage
 \section{Conclusion}\label{sec:summary}
